---
title: "Evaluating the sensitivity of posterior predictions to prior selection"
author: "Jennifer McHenry"
date: "2023-02-23"
output: html_document
---

```{r,include=FALSE}
# Setting up Rstan


# remove.packages(c("rstan", "StanHeaders"))
# if (file.exists(".RData")) file.remove(".RData")
# # #

# install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

# update.packages("rstan")
library(StanHeaders)
library(rstan)
library(collapse)
# install.packages("collapse")

# example(stan_model, package = "rstan", run.dontrun = TRUE)

# rstan_options(auto_write=TRUE)
# install.packages("brms", dependencies = TRUE)
```

```{r,include=FALSE}
# Load required libraries
library(brms)         # Bayesian modeling through Stan
library(tidyverse)    # ggplot, dplyr, %>%, and friends
library(tidybayes)    # Manipulate Stan objects in a tidy way
library(broom)        # Convert model objects to data frames
library(broom.mixed)  # Convert brms model objects to data frames
library(emmeans)      # Calculate marginal effects in even fancier ways
library(patchwork)    # Combine ggplot objects
library(ggokabeito)   # Neat accessible color palette
library(gghalves)     # Special half geoms
library(ggbeeswarm)   # Special distribution-shaped point jittering
library(HDInterval)
library(marginaleffects)
library(performance)
library(loo)
library(bayesplot)



theme_clean <- function() {
  theme_minimal(base_family = "News Cycle") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(face = "bold"),
          axis.title = element_text(face = "bold"),
          strip.text = element_text(face = "bold", size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA),
          legend.title = element_text(face = "bold"))
}


theme_publish <- function(base_size = 12, base_family = "",
                          base_line_size = 0.25, ...) {
  half_line <- base_size / 2
  small_rel <- 0.8
  small_size <- small_rel * base_size
  
  # TODO: replace size with linewidth in `element_rect()`
  theme_bw(base_size = base_size, base_family = base_family, ...) %+replace%
    theme(
      rect = element_rect(fill = "transparent", colour = NA, color = NA,
                          size = 0, linetype = 0),
      text = element_text(family = base_family, face = "plain",
                          colour = "black", size = base_size, hjust = 0.5,
                          vjust = 0.5, angle = 0, lineheight = 0.9,
                          margin = ggplot2::margin(), debug = F),
      
      axis.text = element_text(size = small_size),
      axis.text.x = element_text(margin = ggplot2::margin(t = small_size/4),
                                 vjust = 1),
      axis.text.y = element_text(margin = ggplot2::margin(r = small_size/4), 
                                 hjust = 1),
      axis.title.x = element_text(margin = ggplot2::margin(t = small_size,
                                                           b = small_size)),
      axis.title.y = element_text(angle = 90,
                                  margin = ggplot2::margin(r = small_size,
                                                           l = small_size/4)),
      axis.ticks = element_line(colour = "black", size = base_line_size),
      axis.ticks.length = unit(0.25, 'lines'),
      
      axis.line = element_line(colour = "black", size = base_line_size),
      axis.line.x = element_line(colour = "black", size = base_line_size), 
      axis.line.y = element_line(colour = "black", size = base_line_size), 
      
      legend.spacing = unit(base_size/4, "pt"),
      legend.key = element_blank(),
      legend.key.size = unit(1 * base_size, "pt"),
      legend.key.width = unit(1.5 * base_size, 'pt'),
      legend.text = element_text(size = rel(small_rel)),
      legend.title = element_text(size = rel(small_rel), face = 'bold'),
      legend.position = 'bottom',
      legend.box = 'horizontal',
      
      panel.spacing = unit(1, "lines"),
      panel.background = element_blank(),
      panel.border = element_blank(), 
      # panel.grid.major = element_blank(),
      # panel.grid.minor = element_blank(),
      # 
      strip.text = element_text(size = base_size),
      strip.background = element_rect(fill = NA, colour = "black",
                                      size = 0.125),
      strip.text.x = element_text(face = 'bold', hjust = 0,
                                  margin = ggplot2::margin(b = small_size/2,
                                                           t = small_size/4)),
      strip.text.y = element_text(angle = -90, face = 'bold',
                                  margin = ggplot2::margin(l = small_size/2,
                                                           r = small_size/4)),
      
      plot.margin = unit(c(5,5,0,0), "pt"),
      plot.background = element_blank(),
      plot.title = element_text(face = "bold", size = 1.2 * base_size, 
                                margin = ggplot2::margin(b = half_line),
                                hjust = 0)
    )
}
```

# Bayesian Model Sources
```{r}
# https://vasishth.github.io/bayescogsci/book/ch-remame.html

# https://www.rdocumentation.org/packages/brms/versions/0.9.1/topics/brm

# https://vincentarelbundock.github.io/marginaleffects/articles/brms.html

# https://paul-buerkner.github.io/brms/reference/posterior_summary.html

# https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#different-kinds-of-average-predictions-with-multilevel-models
```


# Data 
```{r,include=FALSE}
C_Production_Collated_DF<-read.csv("final_collated_data/collated_kelp_C_NPP_production_singlemodel_df.csv")

C_prod_rate_model_data <- data.frame(
  ocean= C_Production_Collated_DF$Coast, #Arctic, Atlantic, Pacific
  canopy_type = C_Production_Collated_DF$Canopy_Type,# surface vs subsurface
  site = C_Production_Collated_DF$Site,  # Site identifier
  taxa = C_Production_Collated_DF$Taxa, #species
  year = paste(C_Production_Collated_DF$Start_year,C_Production_Collated_DF$End_year,sep="_"),
  latitude = C_Production_Collated_DF$Latitude_dd,
  ocean_temperature = C_Production_Collated_DF$Mean_SST_BioOracle,
  PAR = C_Production_Collated_DF$Mean_PAR_BioOracle,
  effect = C_Production_Collated_DF$Avg_Production_MgC_ha_y1,  # Site or study level mean
  sd = C_Production_Collated_DF$stdev_Production_MgC_ha_y1,
  source = C_Production_Collated_DF$Reference)%>% # Site or study level sd on the mean 
  mutate(observation_id = 1:n(), 
         # sd=ifelse(sd==0,NA,sd))
          sd=ifelse(is.na(sd)==TRUE,0,sd))%>%
    mutate(taxa=ifelse(taxa=="Hedophyllum nigripes" | taxa=="Laminaria digitata","L. digitata / H. nigripes",taxa))
    # filter(month=="June")


#splitting the data by species
C_prod_model_data_sppsplit <-C_prod_rate_model_data%>%
  group_by(taxa)

C_prod_model_data_sppsplit<-group_split(C_prod_model_data_sppsplit)

```


# Setting up the priors
```{r}
# https://paul-buerkner.github.io/brms/reference/set_prior.html#:~:text=By%20default%2C%20sigma%20has%20a,fixed%20lower%20bound%20of%201%20.
priors1 <- c(prior(student_t(3,0,1), class = Intercept),
             prior(student_t(3,0,1), class = sigma))

priors2 <- c(prior(student_t(3,0,3), class = Intercept),
             prior(student_t(3,0,3), class = sigma))

priors3 <-  c(prior(student_t(3,0,6), class = Intercept),
             prior(student_t(3,0,6), class = sigma))

priors4 <-  c(prior(student_t(3,0,9), class = Intercept),
             prior(student_t(3,0,9), class = sigma))

priors5 <-  c(prior(student_t(3,0,12), class = Intercept),
             prior(student_t(3,0,12), class = sigma))

priors6 <- c(prior(normal(0,0.5), class = Intercept),
             prior(normal(0,0.5), class = sigma))

priors7 <- c(prior(normal(0,1), class = Intercept),
             prior(normal(0,1), class = sigma))

priors8 <-  c(prior(normal(0,5), class = Intercept),
             prior(normal(0,5), class = sigma))

priors9 <-   c(prior(normal(0,10), class = Intercept),
             prior(normal(0,10), class = sigma))

priors10 <-  c(prior(normal(0,20), class = Intercept),
             prior(normal(0,20), class = sigma))

```

# C PRODUCTION RATE MODELS - 
Will start with the species that have the most samples (i.e,. Macrocystis and Nereocystis) and then move on to the "weaker" species. 

## Macrocystis pyrifera
 
```{r,results = FALSE}
Mpyr_C_prod_df <- C_prod_model_data_sppsplit[[5]]

Mpyr.prod.p1 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors1,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Mpyr.prod.p2 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors2,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Mpyr.prod.p3 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~  (1 | year) + (1 |site),
                  prior = priors3,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Mpyr.prod.p4 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors4,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Mpyr.prod.p5 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors5,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Mpyr.prod.p6 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors6,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Mpyr.prod.p7 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors7,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Mpyr.prod.p8 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors8,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)



Mpyr.prod.p9 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors9,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Mpyr.prod.p10 <- brm(data = Mpyr_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors10,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Mpyr.pp.1 <- as.data.frame(avg_predictions(model = Mpyr.prod.p1,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.1$prior <- c("Student T 3,0,1")

Mpyr.pp.2 <- as.data.frame(avg_predictions(model = Mpyr.prod.p2,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.2$prior <- c("Student T 3,0,3")

Mpyr.pp.3 <- as.data.frame(avg_predictions(model = Mpyr.prod.p3,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.3$prior <- c("Student T 3,0,6")

Mpyr.pp.4 <- as.data.frame(avg_predictions(model = Mpyr.prod.p4,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.4$prior <- c("Student T 3,0,9")

Mpyr.pp.5 <- as.data.frame(avg_predictions(model = Mpyr.prod.p5,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.5$prior <- c("Student T 3,0,12")

Mpyr.pp.6 <- as.data.frame(avg_predictions(model = Mpyr.prod.p6,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.6$prior <- c("Normal 0,0.5")

Mpyr.pp.7 <- as.data.frame(avg_predictions(model = Mpyr.prod.p7,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.7$prior <- c("Normal 0,1")

Mpyr.pp.8 <- as.data.frame(avg_predictions(model = Mpyr.prod.p8,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.8$prior <- c("Normal 0,5")

Mpyr.pp.9 <- as.data.frame(avg_predictions(model = Mpyr.prod.p9,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.9$prior <- c("Normal 0,10")

Mpyr.pp.10 <- as.data.frame(avg_predictions(model = Mpyr.prod.p10,by="ocean",newdata=Mpyr_C_prod_df,conf_level = 0.95))
Mpyr.pp.10$prior <- c("Normal 0,20")


Mpyr.pp.sensitivity<-rbind(Mpyr.pp.1,Mpyr.pp.2,Mpyr.pp.3,Mpyr.pp.4,Mpyr.pp.5,Mpyr.pp.6,Mpyr.pp.7,Mpyr.pp.8,Mpyr.pp.9,Mpyr.pp.10)

Mpyr.pp.sensitivity$type <-c("Student","Student","Student","Student","Student","Normal", "Normal", "Normal", "Normal", "Normal")
```


### Comparing the sensitivity of model predictions to prior specifications
```{r}
p1 <-Mpyr.pp.sensitivity%>%
  mutate(prior=factor(prior,levels=c("Student T 3,0,1","Student T 3,0,3","Student T 3,0,6","Student T 3,0,9","Student T 3,0,12","Normal 0,0.5","Normal 0,1","Normal 0,5","Normal 0,10","Normal 0,20")))%>%
  filter(type=="Student")%>%
  ggplot(aes(x = prior, y = estimate,group=type)) + 
  geom_line(col='red') +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
  ylim(0,15)+ggtitle("a. Macrocystis pyrifera")

p2 <-Mpyr.pp.sensitivity%>%
  mutate(prior=factor(prior,levels=c("Student T 3,0,1","Student T 3,0,3","Student T 3,0,6","Student T 3,0,9","Student T 3,0,12","Normal 0,0.5","Normal 0,1","Normal 0,5","Normal 0,10","Normal 0,20")))%>%
  filter(type=="Normal")%>%
  ggplot(aes(x = prior, y = estimate,group=type)) + 
  geom_line(col='red') +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
  ylim(0,15)

macro <- (p1 | p2) + plot_annotation("a. Macrocystis pyrifera")

```

### Comparing the prior to the posterior 
```{r}
# Comparing priors to posteriors
Mpyr_priors <- prior_draws(Mpyr.prod.p1)
Mpyr_post<- as.data.frame(Mpyr.prod.p1)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 0, 0.5") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p2)
Mpyr_post<- as.data.frame(Mpyr.prod.p2)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,1") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p3)
Mpyr_post<- as.data.frame(Mpyr.prod.p3)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,3") +
  xlim(-30,  30) +
  theme_classic()


Mpyr_priors <- prior_draws(Mpyr.prod.p4)
Mpyr_post<- as.data.frame(Mpyr.prod.p4)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,6") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p5)
Mpyr_post<- as.data.frame(Mpyr.prod.p5)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,9") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p6)
Mpyr_post<- as.data.frame(Mpyr.prod.p6)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 0.5") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p7)
Mpyr_post<- as.data.frame(Mpyr.prod.p7)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 1") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p8)
Mpyr_post<- as.data.frame(Mpyr.prod.p8)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 5") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p9)
Mpyr_post<- as.data.frame(Mpyr.prod.p9)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 10") +
  xlim(-30,  30) +
  theme_classic()

Mpyr_priors <- prior_draws(Mpyr.prod.p10)
Mpyr_post<- as.data.frame(Mpyr.prod.p10)

ggplot() +
  geom_density(data = Mpyr_priors, aes(x = Intercept)) +
  geom_density(data = Mpyr_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 20") +
  xlim(-30,  30) +
  theme_classic()
```

## Nereocystis leutkeana

```{r,results = FALSE}
Nleu_C_prod_df <- C_prod_model_data_sppsplit[[5]]

Nleu.prod.p1 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors1,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Nleu.prod.p2 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors2,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Nleu.prod.p3 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~  (1 | year) + (1 |site),
                  prior = priors3,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Nleu.prod.p4 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors4,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Nleu.prod.p5 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors5,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Nleu.prod.p6 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors6,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Nleu.prod.p7 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors7,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Nleu.prod.p8 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors8,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)



Nleu.prod.p9 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors9,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Nleu.prod.p10 <- brm(data = Nleu_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors10,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Nleu.pp.1 <- as.data.frame(avg_predictions(model = Nleu.prod.p1,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.1$prior <- c("Student T 3,0,1")

Nleu.pp.2 <- as.data.frame(avg_predictions(model = Nleu.prod.p2,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.2$prior <- c("Student T 3,0,3")

Nleu.pp.3 <- as.data.frame(avg_predictions(model = Nleu.prod.p3,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.3$prior <- c("Student T 3,0,6")

Nleu.pp.4 <- as.data.frame(avg_predictions(model = Nleu.prod.p4,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.4$prior <- c("Student T 3,0,9")

Nleu.pp.5 <- as.data.frame(avg_predictions(model = Nleu.prod.p5,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.5$prior <- c("Student T 3,0,12")

Nleu.pp.6 <- as.data.frame(avg_predictions(model = Nleu.prod.p6,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.6$prior <- c("Normal 0,0.5")

Nleu.pp.7 <- as.data.frame(avg_predictions(model = Nleu.prod.p7,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.7$prior <- c("Normal 0,1")

Nleu.pp.8 <- as.data.frame(avg_predictions(model = Nleu.prod.p8,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.8$prior <- c("Normal 0,5")

Nleu.pp.9 <- as.data.frame(avg_predictions(model = Nleu.prod.p9,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.9$prior <- c("Normal 0,10")

Nleu.pp.10 <- as.data.frame(avg_predictions(model = Nleu.prod.p10,by="ocean",newdata=Nleu_C_prod_df,conf_level = 0.95))
Nleu.pp.10$prior <- c("Normal 0,20")


Nleu.pp.sensitivity<-rbind(Nleu.pp.1,Nleu.pp.2,Nleu.pp.3,Nleu.pp.4,Nleu.pp.5,Nleu.pp.6,Nleu.pp.7,Nleu.pp.8,Nleu.pp.9,Nleu.pp.10)

Nleu.pp.sensitivity$type <-c("Student","Student","Student","Student","Student","Normal", "Normal", "Normal", "Normal", "Normal")
```

### Comparing the sensitivity of model predictions to prior specifications
```{r}
p1<-Nleu.pp.sensitivity%>%
  mutate(prior=factor(prior,levels=c("Student T 3,0,1","Student T 3,0,3","Student T 3,0,6","Student T 3,0,9","Student T 3,0,12","Normal 0,0.5","Normal 0,1","Normal 0,5","Normal 0,10","Normal 0,20")))%>%
  filter(type=="Student")%>%
  ggplot(aes(x = prior, y = estimate,group=type)) + 
  geom_line(col='red') +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
  ylim(0,15)+ ggtitle("b. Nereocystis leutkeana")

p2<-Nleu.pp.sensitivity%>%
  mutate(prior=factor(prior,levels=c("Student T 3,0,1","Student T 3,0,3","Student T 3,0,6","Student T 3,0,9","Student T 3,0,12","Normal 0,0.5","Normal 0,1","Normal 0,5","Normal 0,10","Normal 0,20")))%>%
  filter(type=="Normal")%>%
  ggplot(aes(x = prior, y = estimate,group=type)) + 
  geom_line(col='red') +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
  ylim(0,15)

nereo <- (p1 | p2) + plot_annotation("b. Nereocystis leutkeana")

```

### Comparing the prior to the posterior 
```{r}
# Comparing priors to posteriors
Nleu_priors <- prior_draws(Nleu.prod.p1)
Nleu_post<- as.data.frame(Nleu.prod.p1)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 0, 0.5") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p2)
Nleu_post<- as.data.frame(Nleu.prod.p2)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,1") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p3)
Nleu_post<- as.data.frame(Nleu.prod.p3)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,3") +
  xlim(-30,  30) +
  theme_classic()


Nleu_priors <- prior_draws(Nleu.prod.p4)
Nleu_post<- as.data.frame(Nleu.prod.p4)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,6") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p5)
Nleu_post<- as.data.frame(Nleu.prod.p5)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,9") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p6)
Nleu_post<- as.data.frame(Nleu.prod.p6)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 0.5") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p7)
Nleu_post<- as.data.frame(Nleu.prod.p7)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 1") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p8)
Nleu_post<- as.data.frame(Nleu.prod.p8)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 5") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p9)
Nleu_post<- as.data.frame(Nleu.prod.p9)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 10") +
  xlim(-30,  30) +
  theme_classic()

Nleu_priors <- prior_draws(Nleu.prod.p10)
Nleu_post<- as.data.frame(Nleu.prod.p10)

ggplot() +
  geom_density(data = Nleu_priors, aes(x = Intercept)) +
  geom_density(data = Nleu_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 20") +
  xlim(-30,  30) +
  theme_classic()
```

## Saccharina latissima

```{r,results = FALSE}
Slat_C_prod_df <- C_prod_model_data_sppsplit[[5]]

Slat.prod.p1 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors1,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Slat.prod.p2 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors2,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Slat.prod.p3 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~  (1 | year) + (1 |site),
                  prior = priors3,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Slat.prod.p4 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors4,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)

Slat.prod.p5 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors5,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Slat.prod.p6 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors6,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Slat.prod.p7 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors7,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Slat.prod.p8 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors8,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)



Slat.prod.p9 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors9,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Slat.prod.p10 <- brm(data = Slat_C_prod_df,
                  family= gaussian,
                  formula = effect | resp_se(`sd`,sigma = TRUE) ~ (1 | year) + (1 |site),
                  prior = priors10,
                  control = list(
                    adapt_delta = .99,
                    max_treedepth = 15),
                  sample_prior=TRUE)


Slat.pp.1 <- as.data.frame(avg_predictions(model = Slat.prod.p1,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.1$prior <- c("Student T 3,0,1")

Slat.pp.2 <- as.data.frame(avg_predictions(model = Slat.prod.p2,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.2$prior <- c("Student T 3,0,3")

Slat.pp.3 <- as.data.frame(avg_predictions(model = Slat.prod.p3,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.3$prior <- c("Student T 3,0,6")

Slat.pp.4 <- as.data.frame(avg_predictions(model = Slat.prod.p4,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.4$prior <- c("Student T 3,0,9")

Slat.pp.5 <- as.data.frame(avg_predictions(model = Slat.prod.p5,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.5$prior <- c("Student T 3,0,12")

Slat.pp.6 <- as.data.frame(avg_predictions(model = Slat.prod.p6,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.6$prior <- c("Normal 0,0.5")

Slat.pp.7 <- as.data.frame(avg_predictions(model = Slat.prod.p7,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.7$prior <- c("Normal 0,1")

Slat.pp.8 <- as.data.frame(avg_predictions(model = Slat.prod.p8,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.8$prior <- c("Normal 0,5")

Slat.pp.9 <- as.data.frame(avg_predictions(model = Slat.prod.p9,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.9$prior <- c("Normal 0,10")

Slat.pp.10 <- as.data.frame(avg_predictions(model = Slat.prod.p10,by="ocean",newdata=Slat_C_prod_df,conf_level = 0.95))
Slat.pp.10$prior <- c("Normal 0,20")


Slat.pp.sensitivity<-rbind(Slat.pp.1,Slat.pp.2,Slat.pp.3,Slat.pp.4,Slat.pp.5,Slat.pp.6,Slat.pp.7,Slat.pp.8,Slat.pp.9,Slat.pp.10)

Slat.pp.sensitivity$type <-c("Student","Student","Student","Student","Student","Normal", "Normal", "Normal", "Normal", "Normal")
```


### Comparing the sensitivity of model predictions to prior specifications
```{r}
p1<- Slat.pp.sensitivity%>%
  mutate(prior=factor(prior,levels=c("Student T 3,0,1","Student T 3,0,3","Student T 3,0,6","Student T 3,0,9","Student T 3,0,12","Normal 0,0.5","Normal 0,1","Normal 0,5","Normal 0,10","Normal 0,20")))%>%
  filter(type=="Student")%>%
  ggplot(aes(x = prior, y = estimate,group=type)) + 
  geom_line(col='red') +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
  ylim(0,15)+ ggtitle("c. Saccharina latissima")

p2<- Slat.pp.sensitivity%>%
  mutate(prior=factor(prior,levels=c("Student T 3,0,1","Student T 3,0,3","Student T 3,0,6","Student T 3,0,9","Student T 3,0,12","Normal 0,0.5","Normal 0,1","Normal 0,5","Normal 0,10","Normal 0,20")))%>%
  filter(type=="Normal")%>%
  ggplot(aes(x = prior, y = estimate,group=type)) + 
  geom_line(col='red') +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
  ylim(0,15)

sacc <- (p1 | p2) 

```


```{r}


pdf("plots/FigureB2.pdf", width = 12, height = 8)
macro  /  nereo / sacc
dev.off()


```
### Comparing the prior to the posterior 
```{r}
# Comparing priors to posteriors
Slat_priors <- prior_draws(Slat.prod.p1)
Slat_post<- as.data.frame(Slat.prod.p1)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 0, 0.5") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p2)
Slat_post<- as.data.frame(Slat.prod.p2)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,1") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p3)
Slat_post<- as.data.frame(Slat.prod.p3)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,3") +
  xlim(-30,  30) +
  theme_classic()


Slat_priors <- prior_draws(Slat.prod.p4)
Slat_post<- as.data.frame(Slat.prod.p4)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,6") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p5)
Slat_post<- as.data.frame(Slat.prod.p5)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Student T 3,0,9") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p6)
Slat_post<- as.data.frame(Slat.prod.p6)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 0.5") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p7)
Slat_post<- as.data.frame(Slat.prod.p7)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 1") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p8)
Slat_post<- as.data.frame(Slat.prod.p8)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 5") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p9)
Slat_post<- as.data.frame(Slat.prod.p9)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 10") +
  xlim(-30,  30) +
  theme_classic()

Slat_priors <- prior_draws(Slat.prod.p10)
Slat_post<- as.data.frame(Slat.prod.p10)

ggplot() +
  geom_density(data = Slat_priors, aes(x = Intercept)) +
  geom_density(data = Slat_post, aes(x = b_Intercept), color = "blue") +
  labs(title = "Prior Distribution vs. Posterior Distribution- Normal 0, 20") +
  xlim(-30,  30) +
  theme_classic()
```

